---
title: "Getting Stated with R"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: "May 14th 2022"
theme: cerulean
---

<!-- For more info on RMarkdown see http://rmarkdown.rstudio.com/ -->

## Name: Mensah Patrick-

### Getting started with R Programming 

### Installing R 
```{r echo=FALSE}
## https://cran.r-project.org/
```

### Installing R-studio
```{r echo=FALSE}
## https://www.rstudio.com/products/rstudio/download/
```

### To get help on "read.table" just type
```{r echo=FALSE}
?read.table ## Reading tables
?anova  ## Anova tables
?lm  ## Fitting linear models 

```
### If you forgot the name you can use the following 
```{r echo=FALSE}

help.search("data input")
help.search("linear model")
help.search("glm")
```

### The find fucntion tells you what package something is located inside 

```{r echo=FALSE, fig.align='center'}
find("lowess")
find("glm")
find("lm")
```


### The apropos function tell you all the names of the search list you want to find. 
```{r echo=FALSE}
apropos("glm")
apropos("lm")
```
### if you want to see some worked examples
```{r echo=FALSE}
 
example("lm")
```

### Here are some useful range of things R can do
```{r echo=FALSE, fig.align='center'}
demo(persp)
demo(graphics)
demo(Hershey)
demo(plotmath)
```

### Installing R packages 

```{r echo=FALSE, fig.align='center' }
install.packages("akima")
install.packages("boot")
install.packages("car")
install.packages("lme4")
installed.packages("meta")
install.packages("mgcv")
install.packages("nlme")
installed.packages("deSolve")
install.packages("R2jags")
install.packages("RColorBrewer")
install.packages("RODBC")
install.packages("rpart")
install.packages("spatstat")
install.packages("spdep")
installed.packages("tree")
```

###. Data Editor. 

```{r echo=FALSE}
library(MASS)
attach(bacteria)
View(bacteria)
```


###. To see what you have created in the current section

```{r echo=FALSE}
objects()
```
###. To see which packages and dataframes are currently attached

```{r echo=FALSE}
search()
```

###. It is important to remove remove any variable name you created after your code. Example 

```{r echo=FALSE}
philant <-c(1,2,3,5,6)
philant
rm(philant)
philant    #not found  
```

###. Detach function
###. Detach fucntion does not mean a dataframe will disappear. it means the variable within these dataframes, example Area, slope are not accessible directly by name. 

```{r echo=FALSE}
detach(worms) 
detach(cars)
detach(philant)
```

###. To get rid of everything including all dataframe. 

```{r echo=FALSE}
rm(list = ls())
```


